A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2016-01-05 docs/discussion_merger_v3.03.tex
Small corrections in text and changes in plot legends.

%Gas accretion - no!
Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population \Wilma{[TO DO: REF]}. However, to form enough stars such that the net rotation of the large and massive core is retrograde, a very large amount of gas would have had to be accreted by J1331---which is not very likely [TO DO: REF].

>>>>

%Gas accretion - no!
Accretion of gas on retrograde orbits and subsequent star formation could lead to a younger and counter-rotating stellar population \Wilma{[TO DO: REF]}. However, to form enough stars such that the net rotation of the large and massive core is retrograde, a very large amount of gas would have had to be accreted by J1331---which is not very likely \Wilma{[TO DO: REF]}.

### 2016-01-05 docs/introduction_v3.02.tex
Edited dynamical modelling results sections.
Small corrections in text and changes in plot legends.

The mass profile at larger galactocentric radii can be probed by gas rotation curves that directly measure the galaxy's circular velocity profile \Wilma{[TO DO: REF]}. However, due to its dissipative nature, gas motions are very sensitive to disturbances by e.g., spiral arms and bars \Wilma{[TO DO: REF]}.

>>>>

The mass profile at larger galactocentric radii can be probed by gas rotation curves that directly measure the galaxy's circular velocity profile (e.g., \citealt{1980ApJ...238..471R})\Wilma{[TO DO: Can I use this here?]}. However, due to its dissipative nature, gas motions are very sensitive to disturbances by e.g., spiral arms and bars (e.g., \citealt{2004dad..book.....S}).

### 2016-01-05 docs/results_JAMwithNFW_v3.02.tex
Started rewriting the discussion.
Small corrections in text and changes in plot legends.

%=======================
\begin{figure*}
\centering
\includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
\caption{Posterior probability distribution sampled with MCMC (red dots and histograms) for a JAM model with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$. Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1})$ (green) and the concentration vs. halo mass relation by \citet{Maccio08} from Equation \eqref{eq:Maccio08} in terms of $v_{200}$ vs. $r_s$ with $1\sigma$ scatter (blue). The MCMC samples are color coded according to their probability (darker red for higher probability); the sample point with the highest probability is marked by a black diamond. The black cross is the mean of the distribution and the ellipses are derived from the covariance of matrix of the sample set and correspond approximately to $1\sigma$ (black solid ellipse) and $2\sigma$ (black dotted ellipse). The histograms of the marginalized 1D distributions are overplotted by the mean (black solid lines) and $1\sigma$ error (black dashed lines), whose values are also quoted in the figure and in Table \ref{tab:modelB4_bestfit}. The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}. \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]} \Wilma{[TO DO: More space between titles and upper axes tick labels.]} \Wilma{[TO DO: Maybe mention also: There are slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the DM contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$), the more velocity anisotropy is needed to reproduce the central dip. As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances, but is also mostly constrained by the prior. ]}}
\label{fig:modelB4_triangle}
\end{figure*}
%=======================

@@

%==============
\begin{figure*}
\centering
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_rms_error_curves.ps}
  \caption{Comparison of the $v_\text{rms}$ data with the best fit JAM models.}
  \label{fig:modelB4_vrms}
\end{subfigure}%
\hspace{.02\textwidth}
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
  \caption{Enclosed mass profile.}
  \label{fig:modelB4_enclMass}
\end{subfigure}
\caption{\Wilma{[TO DO: Rewrite caption]} Best fit JAM model including a NFW halo and velocity anisotropy with parameters given in Table \ref{tab:modelB4_bestfit}. The 12 lines shown correspond to the 12 models randomly drawn from the posterior probability distribution and marked as grey diamonds in Figure \ref{fig:modelB4_triangle}. Overplotted are the Einstein radius (red dotted line) and the effective half-light radius (black dotted line). The blue dashed line marks the radius within which the data and model were fitted. \emph{Panel a)} shows the comparison of the symmetrized $v_\text{rms}$ data (solid blue points) with the best fit JAM models including a NFW halo (red solid lines). Also shown is the non-symmetrized data at larger radii (open blue dots) and an extrapolation of the best fit models, using the same model parameters but the I-band surface brightness MGE for the outer regions of J1331 derived from the Ellipse model (red dashed lines). \emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and DM (grey). \Wilma{[TO DO: make one separate circular velocity plot, that also contains the mass-follows-light with Einstein M/L vcirc and compares it with Aaron's vcirc curve. Ask Aaron for data.]} \emph{Panel c)} shows the corresponding enclosed mass profile. Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint. \Wilma{[TO DO: Replace arcsec with '']} \Wilma{[TO DO: Use $\text{km s}^{-1}$ instead of km/s]} \Wilma{[TO DO: Make two figures from this: vrms (shrinked horizontally) and encl Mass should be first and second panel of one figure, and circular velocity curve should be separate figure. ] \Wilma{[TO DO: Use MGE for the inenr regions in circular velocity plot.]}}}
\label{fig:modelB4_models}
\end{figure*}
%==============

>>>>

%=======================
\begin{figure*}
\centering
\includegraphics[width=0.9\linewidth]{fig/B4_contour_plot_short.ps}
\caption{Posterior probability distribution sampled with MCMC (red dots and histograms) for a JAM model with NFW halo, parametrized by $r_s$ and $v_\text{200}$, a stellar mass distribution generated from the I-band MGE in Table \ref{tab:MGEF814W} and a constant stellar mass-to-light ratio $\Upsilon_\text{I,*}$, and constant velocity anisotropy $\beta_z$. Shown are also the priors used for J1331's NFW halo, $\mathscr{N}(200~\text{km s}^{-1},40~\text{km s}^{-1})$ (green) and the concentration vs. halo mass relation by \citet{Maccio08} from Equation \eqref{eq:Maccio08} in terms of $v_{200}$ vs. $r_s$ with $1\sigma$ scatter (blue). The MCMC samples are color coded according to their probability (darker red for higher probability); the sample point with the highest probability is marked by a black diamond. The black cross is the mean of the distribution and the ellipses are derived from the covariance of matrix of the sample set and correspond approximately to $1\sigma$ (black solid ellipse) and $2\sigma$ (black dotted ellipse). The histograms of the marginalized 1D distributions are overplotted by the mean (black solid lines) and $1\sigma$ error (black dashed lines), whose values are also quoted in the figure and in Table \ref{tab:modelB4_bestfit}. The grey diamonds mark a random sub-selection of 12 samples; the corresponding models are shown in Figure \ref{fig:modelB4_models}. \Wilma{[TO DO: Maybe mention also: There are slight covariances between $\Upsilon_\text{I,*}$,  $r_s$ and $\beta_z$: The smaller the DM contribution in the center (i.e., the larger $\Upsilon_\text{I,*}$), the less concentrated is the halo (i.e., the larger $r_s$), the more velocity anisotropy is needed to reproduce the central dip. As the effect of $v_{200}$ is mostly at larger radii, this parameter doesn't show any covariances, but is also mostly constrained by the prior. ]}}
\label{fig:modelB4_triangle}
\end{figure*}
%=======================

@@

%==============
\begin{figure*}
\centering
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_rms_error_curves.ps}
  \caption{Comparison of the $v_\text{rms}$ data with the best fit JAM models.}
  \label{fig:modelB4_vrms}
\end{subfigure}%
\hspace{.02\textwidth}
\begin{subfigure}{.48\textwidth}
  \centering
  \includegraphics[width=0.9\linewidth]{fig/B4_jam_profiles_errors_short_projmass.ps}
  \caption{Enclosed mass profile.}
  \label{fig:modelB4_enclMass}
\end{subfigure}
\caption{\Wilma{[TO DO: Rewrite caption]} Best fit JAM model including a NFW halo and velocity anisotropy with parameters given in Table \ref{tab:modelB4_bestfit}. The 12 lines shown correspond to the 12 models randomly drawn from the posterior probability distribution and marked as grey diamonds in Figure \ref{fig:modelB4_triangle}. Overplotted are the Einstein radius (red dotted line) and the effective half-light radius (black dotted line). The blue dashed line marks the radius within which the data and model were fitted. \emph{Panel a)} shows the comparison of the symmetrized $v_\text{rms}$ data (solid blue points) with the best fit JAM models including a NFW halo (red solid lines). Also shown is the non-symmetrized data at larger radii (open blue dots) and an extrapolation of the best fit models, using the same model parameters but the I-band surface brightness MGE for the outer regions of J1331 derived from the Ellipse model (red dashed lines). \emph{Panel b)} shows the circular velocity curve of the total mass (green), and separately the contribution of the stellar mass (yellow, again generated from the MGE in Table \ref{tab:MGEF814W}) and DM (grey). \emph{Panel c)} shows the corresponding enclosed mass profile. Overplotted is also the Einstein mass at the Einstein radius with a 10\% error, which was used in the fit as an additional constraint.}
\label{fig:modelB4_models}
\end{figure*}
%==============

### 2016-01-05 docs/results_JAMwithSB_v3.01.tex
Small corrections in text and changes in plot legends.

\paragraph{JAM with lens mass model.} We make an independent prediction for the $v_\text{rms}$ curve by evaluating Equation \Wilma{[TO DO]} (with $\beta_z = 0$) for the lens mass model in Table \ref{tab:bestfitlensmodel} ($\alpha = 1$, flat rotation curve). In addition, we also calculate a  $v_\text{rms}$ curve for a lens model which was found analogously, but assumed a slightly rising rotation curve slope of $\alpha=1.1$. The predictions are compared with the data in Figure \ref{fig:JAM_modelL}. The agreement within $R' \sim 3''$ is striking: The $\alpha > 1$ model recreates the observed central dip, while the $\alpha = 1$ model fits the wings around $R_\text{eff}$. This is in concordance with observations in other galaxies. For $R'> R_\text{eff}$ we would expect $\alpha<1$. Our lensing model assumes $\alpha(R')=\text{const}$, although Figure \ref{fig:JAM_modelL} suggests, that a model with variable $\alpha(R')$ might fit even better, and maybe also reproduce the sharp drop in $v_\text{rms}$ around $R' \sim 3''$. We note however, that the most reliable constraint is around $R_\text{ein}$. Outside of $R_\text{ein}$ lensing models are only extrapolations.

@@

\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
  \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in Section \ref{sec:results_lensing}. \Wilma{[TO DO: Add Note that outside Rein extrapolation.]} The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the green line is a best fit lens model found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$. For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.The red and black dotted lines are the Einstein radius and the effective half-light radius, respectively.}
  \label{fig:JAM_modelL}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (solid red line) assuming mass-follows-light and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total I-band mass-to-light ratio found from dynamics, which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$. The ``best'' fit is $\Upsilon_\text{I,tot}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range. This is obviously not a good model.}
  \label{fig:JAM_modelA2}
\end{figure}

>>>>

\paragraph{JAM with lens mass model.} We make an independent prediction for the $v_\text{rms}$ curve by evaluating Equation \ref{eq:explicitLOSvelCap} (with $\beta_z = 0$) for the lens mass model in Table \ref{tab:bestfitlensmodel} ($\alpha = 1$, flat rotation curve). In addition, we also calculate a  $v_\text{rms}$ curve for two lens models which were found analogously, but assumed a slightly rising (falling) rotation curve slope of $\alpha=1.1$ ($\alpha=0.9$). The predictions are compared with the data in Figure \ref{fig:JAM_modelL}. While the most reliable constraint is around $R_\text{ein}$, the agreement within $R' \sim 3''$ is still striking: The $\alpha > 1$ model recreates the observed central dip, while the $\alpha = 1$ model fits the wings around $R_\text{eff}$. This is in concordance with observations in other galaxies. For $R'> R_\text{eff}$ we would expect $\alpha<1$---and the lensing model for $\alpha=0.9$ has indeed a slightly dropping $v_\text{rms}$ around $R_\text{eff}$, like the data. A definite comparison in this regime is however difficult as the lens models are just extrapolations outside of $R_\text{ein}$. While our lensing model assumes $\alpha(R')=\text{const}$, Figure \ref{fig:JAM_modelL} suggests, that a model with variable $\alpha(R')$ could fit even better. Overall the lensing model is in very good agreement with the $v_\text{rms}$ data within $R' \sim 3''$---even though it was derived completely independently.

@@

\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
  \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in Section \ref{sec:results_lensing} (red lines). The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the red dashed and dash-dotted lines are best fit lens models found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$ and $0.9$, respectively. For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$. The most reliable constraints are around the Einstein radius (vertical red dotted line); outside of it the JAM model is just an extrapolation.}
  \label{fig:JAM_modelL}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (orange line) assuming mass-follows-light and with two free parameters: $\Upsilon_\text{I,tot}^\text{dyn}$, the total I-band mass-to-light ratio found from dynamics, which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$. The ``best'' fit is $\Upsilon_\text{I,tot}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range. This is obviously not a good model.}
  \label{fig:JAM_modelA2}
\end{figure}

### 2016-01-05 docs/results_lensing_v3.01.tex
Small corrections in text and changes in plot legends.

\Wilma{[TO DO: Intro Sentence]}

@@

\begin{figure}
\centering
  \includegraphics[width=\linewidth]{fig/lens_all_in_one.ps}
\caption{Lensing model (Table \ref{tab:bestfitlensmodel}) found as best fit to the image positions. In the background we show the central region of J1331 in the F450W filter, subtracted by an IRAF \emph{ellipse} model of the F450W surface brightness and smoothed to remove noise smaller than the PSF. The brightness peaks of the four lensing images and the galaxy center (Table \ref{tab:lenspos}) are marked as red dots. For the best fit lens model we show the Einstein radius (red dotted circle) and the critical curve (red solid line), which are located in the lens plane. We also show the caustic (green solid line) corresponding to the critical curve and best fit source position (green dot), which are located in the source plane. For $\alpha=1$ the critical curve is a contour of constant surface density of the mass model. The grey  lines show contours of the time delay surface given by Equation \eqref{eq:timedelay}. Not only the position of the extrema, but also their shape is consistent with the observed, extended images, even though we did not use information about the image shape in the analysis.}
\label{fig:???}
\end{figure}

@@

\paragraph{Best fit lens model.} We fit the lens mass model to the image positions in Table \ref{tab:lenspos} by minimizing $\chi^2 = \chi_\text{lens}^2 + \chi_\text{shape}^2$ (see Equations \eqref{eq:chi2lens}-\eqref{eq:chi2total}). The best fit parameters are given in the first column of Table \ref{tab:bestfitlensmodel}. Figure \ref{fig:lensbestfiteinsteincurves} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position. In this case, where $\alpha=1$, the (tangential) critical curve is also an equidensity contour of the galaxy model \citep{EvansWitt}, which appears to have an elliptical mass distribution. The source is located close to a cusp of the diamond-shaped caustic: a lensing configuration for which we indeed expect four images. Figure \ref{fig:lensbestfittimedelay} overplots the (smoothed) residuals from the F450W image subtracted by an IRAF \emph{ellipse} brightness model with the contours of the best fit model's time delay surface. This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source.

@@

\begin{figure*}
\centering
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_surface_brightness.ps}
  \caption{Observed light distribution.}
  \label{fig:lenscomparelight}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_surface_density.ps}
  \caption{Predicted mass distribution.}
  \label{fig:lenscomparemass}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/paper_lensmass_brightness_compare.ps}
  \caption{Comparison of mass and light.}
  \label{fig:lenscompareboth}
\end{subfigure}
\caption{Comparison of the observed F814W/I-band surface brightness distribution (Panel (a) and orange contours) and predicted mass distribution from lensing constraints (Panel (b) and pink contours). To allow for a qualitative comparison of the contours in Panel (c), the light distribution was turned into a mass distribution by multiplication with the total mass-to-light ratio inside the Einstein radius $\Upsilon_\text{I,tot}^\text{ein}$ in Table \ref{tab:einsteinML}. The Einstein radius is overplotted as red dotted circle. The uncertainties in the mass model in the second column of Table \ref{tab:bestfitlensmodel} were translated into random Monte Carlo noise in the mass contours. The smooth black contours correspond to the best fit model in the first column of Table \ref{tab:bestfitlensmodel}. The background in Panel (c) shows again the surface brightness subtracted center of the galaxy to make the lensing images visible. \Wilma{[TO DO: use $\Upsilon_\text{I,tot}^\text{ein}$ on colorbar]}}
\label{fig:lenslightcompareALL}
\end{figure*}

@@

We estimate the total mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} \equiv M_\text{ein} / L_\text{I,ein}$. For this, we integrate the MGE in Table \ref{tab:MGEF814W} to get the total I-band luminosity within the Einstein radius $L_\text{I,ein} = 1.40\cdot 10^{10} L_\odot$. The corresponding Einstein mass-to-light ratio is therefore $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$. This is consistent with or slightly larger than the stellar mass-to-light ratio assuming a Salpeter IMF $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}).

@@

\Wilma{[TO DO: Make sure IMF is introduced somewhere.]}

>>>>

In this section we use the gravitational lensing formalism summarized in Section \ref{sec:lensing_theo} to fit a scale-free galaxy mass model to the positions of the lensing images observed in J1331's central region.

@@

\begin{figure}
\centering
  \includegraphics[width=\linewidth]{fig/lens_all_in_one.ps}
\caption{Lensing model (Table \ref{tab:bestfitlensmodel}) found as best fit to the image positions. In the background we show the central region of J1331 in the F450W filter, subtracted by an IRAF \emph{ellipse} model of the F450W surface brightness and smoothed to remove noise smaller than the PSF. The brightness peaks of the four lensing images and the galaxy center (Table \ref{tab:lenspos}) are marked as red dots. For the best fit lens model we show the Einstein radius (red dotted circle) and the critical curve (red solid line), which are located in the lens plane. We also show the caustic (green solid line) corresponding to the critical curve and best fit source position (green dot), which are located in the source plane. For $\alpha=1$ the critical curve is a contour of constant surface density of the mass model. The grey  lines show contours of the time delay surface given by Equation \eqref{eq:timedelay}. Not only the position of the extrema, but also their shape is consistent with the observed, extended images, even though we did not use information about the image shape in the analysis.}
\label{fig:bestfitlensmodel}
\end{figure}

@@

\paragraph{Best fit lens model.} We fit the lens mass model to the image positions in Table \ref{tab:lenspos} by minimizing $\chi^2 = \chi_\text{lens}^2 + \chi_\text{shape}^2$ (see Equations \eqref{eq:chi2lens}-\eqref{eq:chi2total}). The best fit parameters are given in the first column of Table \ref{tab:bestfitlensmodel}. Figure \ref{fig:bestfitlensmodel} shows the corresponding critical curve, caustic and Einstein radius, and the best fit source position. In this case, where $\alpha=1$, the (tangential) critical curve is also an equidensity contour of the galaxy model \citep{EvansWitt}, which appears to have an elliptical mass distribution. The source is located close to a cusp of the diamond-shaped caustic: a lensing configuration for which we indeed expect four images. Figure \ref{fig:bestfitlensmodel} also shows the (smoothed) residuals from the F450W image subtracted by an IRAF \emph{ellipse} brightness model and the contours of the best fit model's time delay surface. This demonstrates that, although we did not include any information about the shape of the lensing images in the fit, it is consistent with the predicted distortion for an extended source.

@@

\begin{figure*}
\centering
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_surface_brightness.ps}
  \caption{Observed light distribution.}
  \label{fig:lenscomparelight}
\end{subfigure}%
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/lens_surface_density.ps}
  \caption{Predicted mass distribution.}
  \label{fig:lenscomparemass}
\end{subfigure}
\begin{subfigure}{.3\textwidth}
  \centering
  \includegraphics[width=.9\linewidth]{fig/paper_lensmass_brightness_compare.ps}
  \caption{Comparison of mass and light.}
  \label{fig:lenscompareboth}
\end{subfigure}
\caption{Comparison of the observed F814W/I-band surface brightness distribution (Panel (a) and orange contours) and predicted mass distribution from lensing constraints (Panel (b) and pink contours). To allow for a qualitative comparison of the contours in Panel (c), the light distribution was turned into a mass distribution by multiplication with the total mass-to-light ratio inside the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$. The Einstein radius is overplotted as red dotted circle. The uncertainties in the mass model in the second column of Table \ref{tab:bestfitlensmodel} were translated into random Monte Carlo noise in the mass contours. The smooth black contours correspond to the best fit model in the first column of Table \ref{tab:bestfitlensmodel}. The background in Panel (c) shows again the surface brightness subtracted center of the galaxy to make the lensing images visible.}
\label{fig:lenslightcompareALL}
\end{figure*}

@@

We estimate the total mass-to-light ratio within the Einstein radius $\Upsilon_\text{I,tot}^\text{ein} \equiv M_\text{ein} / L_\text{I,ein}$. For this, we integrate the MGE in Table \ref{tab:MGEF814W} to get the total I-band luminosity within the Einstein radius $L_\text{I,ein} = 1.40\cdot 10^{10} L_\odot$. The corresponding Einstein mass-to-light ratio is therefore $\Upsilon_\text{I,tot}^\text{ein} = 5.56 \Upsilon_{I,\odot}$. This is consistent with or slightly larger than the stellar mass-to-light ratio assuming a Salpeter initial mass function (IMF) $\Upsilon_\text{I,*}^\text{sal} = 4.7 \pm 1.2$ according to \citet{SWELLSI} and Table \ref{tab:previousresults} (see also discussion in Section \ref{sec:MLdiscussion}).

@@

### 2016-01-05 docs/results_photometry_v3.02.tex
Small corrections in text and changes in plot legends.

In this section we construct a model for the J1331's intrinsic light distribution in terms of MGEs (see Section \ref{sec:MGE_theo}). We use the HST image in the F814W (I-band) filter (Figure \ref{fig:F814W}) because J1331's central stellar component appears at longer wavelengths (a) smoother and more extended than in the F450W filter (Figure \ref{fig:F450W}), as it is less sensitive to young clumpy star-forming regions, (b) much brighter than the bluish lensing images, and (c) the imaging is less prone to extinction.

@@

%============================================================================
\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
  \caption{MGE for J1331's inner regions.}
 \label{fig:MGEinnerRegions}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
  \caption{MGE for J1331's outer regions.}
 \label{fig:MGEouterRegions}
\end{subfigure}%
\caption{MGEs for J1331's surface brightness distribution. Comparison of contours with constant F814W surface brightness (orange lines) with the corresponding iso-brightness contours of the best fit MGE, convolved with the PSF in Table \ref{tab:MGEF814W}, (gray lines). The black line has a length of $10''$ and it's orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}. For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed line. \emph{Panel (a)} Central regions of J1331. The MGE model is a good representation of the galaxy's light distribution along the major axis within $\sim 5''$. Its parameters are given in Table \ref{tab:MGEF814W}. This MGE is used as model for the stellar tracer distribution in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}. \emph{Panel (b)} Outer regions of J1331. The orange lines indicate here contours of a smooth IRAF \emph{ellipse} fit to J1331 in the F814W filter; the gray lines are the corresponding best fit MGE. The green box corresponds to the image section shown in Panel (a). This MGE is not used for dynamical modelling, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms). We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions. \Wilma{[TO DO: No dotted line]}}
\end{figure*}
%============================================================================

>>>>

In this section we construct a model for the J1331's intrinsic light distribution in terms of MGEs (see Section \ref{sec:MGE_theo}). We use the HST image in the F814W (I-band) filter (Figure \ref{fig:F814W}) because J1331's central stellar component appears at longer wavelengths (i) smoother and more extended than in the F450W filter (Figure \ref{fig:F450W}), as it is less sensitive to young clumpy star-forming regions, (ii) much brighter than the bluish lensing images, and (iii) the imaging is less prone to extinction.

@@

%============================================================================
\begin{figure*}
\centering
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\columnwidth]{fig/1331F814Wsci_MGE_M.ps}
  \caption{MGE for J1331's inner regions.}
 \label{fig:MGEinnerRegions}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
  \centering
  \includegraphics[width=.8\columnwidth]{fig/1331F814W_MGE_disk_L.ps}
  \caption{MGE for J1331's outer regions.}
 \label{fig:MGEouterRegions}
\end{subfigure}%
\caption{MGEs for J1331's surface brightness distribution. Comparison of contours with constant F814W surface brightness (orange lines) with the corresponding iso-brightness contours of the best fit MGE, convolved with the PSF in Table \ref{tab:MGEF814W}, (gray lines). The black line has a length of $10''$ and it's orientation corresponds to the galaxy's position angle as found in Table \ref{tab:galaxyparameters}. For comparison the Einstein radius as found in Table \ref{tab:bestfitlensmodel}  is indicated as red dashed line. \emph{Panel (a)} Central regions of J1331. The MGE model is a good representation of the galaxy's light distribution along the major axis within $\sim 5''$. Its parameters are given in Table \ref{tab:MGEF814W}. This MGE is used as model for the stellar tracer distribution in the dynamical Jeans modelling in Sections \ref{sec:results_JAM_SB} and \ref{sec:results_JAM_NFW}. \emph{Panel (b)} Outer regions of J1331. The orange lines indicate here contours of a smooth IRAF \emph{ellipse} fit to J1331 in the F814W filter; the gray lines are the corresponding best fit MGE. The green box corresponds to the image section shown in Panel (a). This MGE is not used for dynamical modelling, because the dynamics in the outer regions are strongly affected by non-axisymmetries (e.g., spiral arms). We use it, however, to estimate the galaxy's total luminosity and effective radius, and to get a prediction for the dynamics of the outer regions.}
\end{figure*}
%============================================================================
